The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-21 project/paper/method-of-moments.tex
Reworded central moments issue a little.

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
and third central moments of $B$ and $Y$.

\subsection{The Central Moments of the Binomial}

@@

\subsection{The Central Moments of the Skew Normal}

@@

To derive our approximation, we set the central moments of our two
distributions equal to each other and, taking $n$ and $p$ as constants, solve
for $\mu$, $\sigma$ and $\lambda$:

>>>>

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
is, by comparing the first, second, and third moments about the mean (also
referred to as central moments) of $B$ and $Y$.

\subsection{The Moments of the Binomial}

@@

\subsection{The Moments of the Skew Normal}

@@

To derive our approximation, we set the above moments of our two distributions
equal to each other and, taking $n$ and $p$ as constants, solve for $\mu$,
$\sigma$ and $\lambda$:
